R for Clinical Study Reports and Submission

### 2021-10-12 index.Rmd

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
```

@@

Welcome to R for clinical study reports and submission. 
Clinical study reports (CSR) are essential parts of clinical trial development. 
A CSR is an "integrated" full scientific report of an individual clinical trial.

The [ICH E3: structure and content of clinical study reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf) 
provides guidance to assist sponsors in the development of a CSR. 
In this book, you will learn how to use R to prepare a CSR and how to submit it to regulatory agencies.

**This is the work-in-progress draft of the book.**

## List of Authors and Contributors {-}

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"), 
                  person("Aiming", "Yang", role = "ctr"),
                  person("Steven", "Haesendonckx", role = "ctr"))
```

@@

- Author: contribute the majority content of at least one chapter. 
- Contributor: [contribute at least one commit to the source code](https://github.com/elong0527/r4csr)

>>>>

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
library(pkglite)
```

@@

Welcome to R for clinical study report and submission. 
Clinical study reports (CSR) are the essential part of clinical trials development. 
a CSR is an "integrated" full scientific report of an individual clinical trial.

The [ICH E3: strcuture and content of clinical study reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf) 
provide guidance to assist sponsors in the development of a CSR. 
In this book, you will learn how to use R to prepare CSR and submit to regulatory agency.

This is the work-in-progress draft of the book.

## List of Authors and Contributors

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"))
```

@@

- Author: contribute majority content of at least one chapter. 
- Contributor: [contribute at least one commit to the source code](https://stash.merck.com/projects/BARDS/repos/r4csr/browse)
